The Gaia-ESO Survey: Combined estimates from multiple stellar analysis pipelines

### 2016-10-14 article/ms.tex
foo
stuff

\begin{itemize}
    \item   \emph{The uncertainties reported by each node are incorrect.}
            This assumption is based on a cursory examination of the data:
            some nodes do not provide uncertainties in stellar parameters, and
            the uncertainties reported by some nodes could vary in percent by
            two orders of magnitude. Therefore, we assume that each node only
            provides a point estimate for astrophysical parameters.

@@

            \noindent{}where $\epsilon$ represents the noise in the estimate.

    \item   \emph{The unbiased stellar parameters from any two nodes are correlated.}
            After accounting for individual node biases, we assume that the 
            stellar parameters reported by any two nodes will be correlated
            to some degree. The level of correlation between two nodes is unknown.
            This assumption arises from commonalities that led to the estimates from
            each node. Specifically: all nodes are instructed to use a common list 
            of line transitions, the same MARCS model photospheres, some nodes employ
            similar methods (e.g., spectral synthesis), and all nodes derive their 
            estimates from the same data (in some instances, even the same 
            continuum-normalized spectra are used).

@@

    \item   \emph{There are gaps in the data.} 
            No spectrum is guaranteed to have stellar parameters reported by all
            nodes. This assumption is a consequence of the different expertise in
            \gaiaeso: no node or method is expert across the entire range of parameter
            space explored. If stellar parameters are not reported, then the reason 
            must be specified through a \texttt{TECH} flag (see Section \ref{sec:flags}
            on flag usage).

    \item   \emph{Random uncertainties in stellar parameters will increase with
            decreasing S/N ratio.}

@@

\end{itemize}

>>>>

\begin{enumerate}
    \item   \emph{The uncertainties reported by each node are incorrect.}
            This assumption is based on a cursory examination of the data:
            some nodes do not provide uncertainties in stellar parameters, and
            the uncertainties reported by some nodes could vary in percent by
            two orders of magnitude. Therefore, we assume that each node only
            provides a point estimate for astrophysical parameters.

@@

            \noindent{}where $\epsilon$ represents the noise in the estimate. As per
            assumption (1), we assert that the distribution of $\epsilon$ is unknown
            for each node.

    \item   \emph{The unbiased stellar parameters from any two nodes are correlated.}
            After accounting for individual node biases, we assume that the stellar 
            parameters reported by any two nodes will be correlated to some degree. 
            The level of correlation between two nodes is unknown \emph{a priori}.
            This assumption arises from commonalities that led to the estimates from
            each node. Specifically: all nodes are instructed to use a common list 
            of line transitions, the same MARCS model photospheres. Moreover, some 
            nodes employ similar methods (e.g., spectral synthesis), and importantly
            \emph{all} nodes derive their estimates from the same data (in some 
            instances, even the same continuum-normalized spectra are used).

@@

    \item   \emph{There are missing data.} 
            No spectrum is guaranteed to have stellar parameters reported by all
            nodes. This assumption is a consequence of the different expertise in
            \gaiaeso: no node or method is expert across the entire range of parameter
            space explored. If stellar parameters are not reported, then the reason 
            must be specified with a technical flag (\texttt{TECH}; see Section 
            \ref{sec:technical-flags}).

    \item   \emph{Random uncertainties in stellar parameters will increase with
            decreasing S/N ratio.}
            Specifically we assume that the random uncertainty $\sigma_{rand}$ will
            increase as,

            \begin{eqnarray}
                \sigma_{rand,node} = \frac{\alpha_{node}}{\sqrt{S/N}}
            \end{eqnarray}

            \noindent{}where $S/N$ is the signal-to-noise ratio, and $\alpha$ is
            unknown for each node.

@@

\end{enumerate}
